First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-08 eg6-letters/coherent/dvcs_he4_prl.tex
minor corrections after Nathan suggestions

The coherent nuclear DVCS channel is experimentally difficult due to  
its small cross section and the necessity to ensure the target remains 
intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on 
$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes the photon-quark 
interaction and is calculable with perturbative QED.  The non-perturbative 
part is parametrized in terms of GPDs, which embed the partonic structure of 
the hadron. The GPDs depend on the three variables $x$, $\xi$ and $t$, which are 
indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
$\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
transferred to the target, however $x$ cannot be experimentally 
accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
Factors (CFF) \cite{Guidal:2013rya} defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ the GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

@@

We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
$\mathcal{H}_A$, together with theoretical calculations from two models, 
labelled {\em convolution} and {\em off-shell}. In the convolution 
model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
non-relativistic non-interacting nucleons, where these nucleons interact 
independently with the probe. The convolution/dual model is based on nucleon GPDs from 
the dual parametrization \cite{Guzey:2006xi}, where the convolution/VGG uses nucleon GPDs  
from the VGG model and is based on the double distributions ansatz 
\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on the 
impulse approximation and uses advanced spectral functions of  
nuclei that account for all configurations of the final nuclear system and the 
binding effects between the nucleons.
[These need to be renamed on the figure, it does not make sense to call differently
models that are identical. We should also request the projections from Vadim
model: hep-ph/0509158.]

The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
from the beam spin asymmetry is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $-t$ are in agreement 
with the theoretical calculations. One can see a difference between the 
precision of the extracted imaginary and real parts, which is expected from
equation \ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. 
While these results are not precise enough to discriminate between the models,
they are very promising for future exeperiments and demonstrate our ability
to directly extract the CFF of the helium nucleus in a completely model
independent way.

>>>>

The coherent nuclear DVCS channel, $eA \rightarrow e' A' \gamma$, is 
experimentally difficult due to  its small cross section and the necessity to 
ensure the target remains intact while emitting a hard photon.  Figure 
\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on $^4$He.  
Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes the photon-quark 
interaction and is calculable with perturbative QED.  The non-perturbative 
part is parametrized in terms of GPDs, which embed the partonic structure of 
the hadron. The GPDs depend on the three variables $x$, $\xi$ and $t$, which are 
indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
$\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
transferred to the target, however $x$ cannot be experimentally 
accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
Factors (CFF) \cite{Guidal:2013rya} defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ the GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

@@

We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
$\mathcal{H}_A$, together with theoretical calculations from two models, 
labelled {\em convolution} and {\em off-shell}. In the convolution 
model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
non-relativistic and non-interacting nucleons, where these nucleons interact 
independently with the probe. The convolution/dual model is based on nucleon 
GPDs from the dual parametrization \cite{Guzey:2006xi}, where the 
convolution/VGG uses nucleon GPDs  from the VGG model and is based on the 
double distributions ansatz \cite{DD_model}. The off-shell model 
\cite{GonzalezHernandez:2012jv} relies on the impulse approximation and uses 
advanced spectral functions of  nuclei that account for all configurations of 
the final nuclear system and the binding effects between the nucleons.
[These need to be renamed on the figure, it does not make sense to call differently
models that are identical. We should also request the projections from Vadim
model: hep-ph/0509158.]

The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
from the beam spin asymmetry is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $-t$ are in agreement 
with the theoretical calculations. One can see a difference between the 
precision of the extracted imaginary and real parts, which is expected from
equation \ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. 
While these results are not precise enough to discriminate between the models,
they are very promising for future experiments and demonstrate our ability
to directly extract the CFF of the helium nucleus in a completely model
independent way.
